Correlation among smart grid actors

### 2015-07-23 Article.tex
intro simplification

In this paper, we focus on these "\textit{nodes}" in the distribution network that can produce and consume electricity. More precisely, we consider a set of agents that own both renewable distributed energy ressources (DER) and electrical loads. The production of an agent can be, of course, used to meet its own demand, but in cases where it is over-producing, we consider that it has the possibility to inject, against financial compensation, its extra-production in the grid. Such an agent model is known as a "\textit{prosumer}" \cite{Rathnayaka2012} (and will be called accordingly in this paper). The primary objective of this work is to mix the interests of the grid operator with the ones of the prosumers in a single utility function. While the latters intend to maximize their benefits with higer production contracts, the operator primary concerns are linked to the quality and stability of the injections. The coalitions that we wish to form should thus be both stable and productive as to satisfy both parts. This compromise can be difficult to obtain in real situations, especially when renewable generation and complex spatiotemporal correlation relationships come into play.

As beautiful as this distributed participatory production scenario seems to be, the constraints necessary for the electrical grid to remain in a stable state forbid any anarchic system where prosumers inject power without proper control. Actually the architecture and control of such a distributed grid creates numerous interdisciplinary challenges. In this paper, the envisaged solution for organizing such a multi-producers system consists in extending the kind of market environement discussed in the previous section. Participating aggregators estimate a production capacity for an upcoming period of time and announce it on the market. If a contract between the grid and a participant is bought, the latter commits to injecting exactly, at any time of the contracted period, the announced amount of power, under financial penalities if it fails.

In this paper, we consider that the production of a prosumer comes from renewables. Contracts are therefore based on predictions and come with a given amount of risk due to the intermittent nature of most renewables. Using storage as buffers in order to reduce riks is a popular approach. Actually, a whole branch of the smart grid litterature is even studying the possibility to use electric vehicles as moving storage capacities for stabilizing the grid. Without storage and proper control, the over-producing state of the agents, and thus the power they inject in the grid, might be rather unstable. This is clearly unacceptable for the grid operator that cannot ensure system stability if it has to deal with numerous small unpredictable entities.

Forming coalitions/aggregations is an envisaged solution to both the number of entities sollicitating the operator, and their high variabilities. Indeed, it has been argued that using a multi-level aggregators architecture for the control could lead to better performances on the communication side, since an aggregator can be considered as a single node by the level above it. On the other hand, it is well-known that diversification of the assets is a way of minimizing risks when constructing a portfolio. One thus expect a more stable and predictable energy production for a coalition than for a single agent. Nevertheless, all coalitions are obviously not equally stable or productive, which means that special attention should be paid to the aggregation step.

Furthermore, in our settings, since the prosumers have both a consumption and a production component, each depending on location and time, the diversification of the aggregations seems not trivial. This is a central topic of the present paper : given N prosumers, what coalitions should be formed so that the compromise between expected production and variability is optimized ?

We will see that variability in the aggregated productions can be quantified to a certain extent by the correlation among the agents forming the coalitions. Understanding the correlation reliationships among the agents can thus give an indication about what coalitions to form and how much they should sell. More precisely, we use a graph representation of the correlation structure to gain insight about the expected production to risk ratios of different coalitions. We build a framework in which the system operator has the possibility of specifying both a maximum amount of risk and a minimum production acceptable to enter the market. Based on predictions, coalitions can decide wether or not to enter and what power quantities they are willing to provide. Of course, coalitions failing at fulfilling their obligations during the contracted period of time (because of bad forecasts, unexpected rare events, or intentional false information) will be exposed to financial penalities.

Because agents are susceptible to fail for diverse reasons, the impact on the system's stability is critical. The propensy of a system to undertake these failures is often refered to as its resilience \cite{Pahwa}. Once formed, we also investigate in this paper the resilience of the coalitions when prosumers fail. Despite the fact that losing agents is usually detrimental to the coalitions, we will see that, with our algorithm, coalitions tend to be less impacted by random failures.

>>>>

In this paper, we focus on these "\textit{nodes}" in the distribution network that can produce and consume electricity. More precisely, we consider a set of agents that own both renewable distributed energy ressources (DER) and electrical loads. The production of an agent can be, of course, used to meet its own demand, but in cases where it is over-producing, we consider that it has the possibility to inject, against financial compensation, its extra-production in the grid. Such an agent model is known as a "\textit{prosumer}" \cite{Rathnayaka2012} (and will be called accordingly in this paper). A key point of this work is to mix the interests of the grid operator with the ones of the prosumers in a single utility function. While the latters intend to maximize their benefits with higer production contracts, the operator primary concerns are linked to the quality and stability of the injections. The coalitions that we wish to form should thus be both stable and productive as to satisfy both parts. This compromise can be difficult to obtain in real situations, especially when renewable generation and complex spatiotemporal correlation relationships come into play.

More precisely, in our model, any entity that whishes to sell its production on some energy market has to estimate and announce a production capacity for an upcoming period of time. If a contract is bought, the entity commits to injecting exactly, at any time of the contracted period, the announced amount of power, under financial penalities if it fails. Since prosumers use exclusively renewables, contracts come naturally with some amount of risk due to the intermittent nature of most renewables. Using storage as buffers in order to reduce riks is a popular approach. Actually, a whole branch of the smart grid litterature is even studying the possibility to use electric vehicles as moving storage capacities for stabilizing the grid. Without storage and proper control, the over-producing state of the agents, and thus the power they inject in the grid, might be rather unstable. This is clearly unacceptable for the grid operator that cannot ensure system stability if it has to deal with numerous small unpredictable entities.

Forming coalitions/aggregations is an envisaged solution to both the number of entities sollicitating the operator, and their high variabilities. Indeed, it has been argued that using a multi-level aggregators architecture for the control could lead to better performances on the communication side, since an aggregator can be considered as a single node by the level above it. On the other hand, it is well-known that diversification of the assets is a way of minimizing risks when constructing a portfolio. One thus expect a more stable and predictable energy production for a coalition than for a single agent. Nevertheless, all coalitions are obviously not equally stable or productive, which means that special attention should be paid to the aggregation step. Recall that prosumers have both a consumption and a production component, each depending on location and time, meaning that there are complex underlying correlations between the agents. This is indeed a central topic of the present paper : given N prosumers, what coalitions should be formed so that the compromise between expected production and variability is optimized ?

We will see that variability in the aggregated productions can be quantified to a certain extent by the correlation among the agents forming the coalitions. Understanding the correlation reliationships among the agents can thus give an indication about what coalitions to form and how much they should sell. More precisely, we use a graph representation of the correlation structure to gain insight about the expected production to risk ratios of different coalitions. We build a framework in which the system operator has the possibility of specifying both a maximum amount of risk and a minimum production acceptable to enter the market. We then propose a graph heuristic that uses decorrelated cliques in order to form diversified productive and stable coalitions, and we compare the results with other formation strategies (see section \ref{sec:results}).

Furthermore, because agents are susceptible to fail for diverse reasons, the propensy of a system to undertake these failures is critical \cite{Pahwa}. We therefore investigate in this paper the resilience of the coalitions when prosumers fail. Despite the fact that losing agents is usually detrimental to the coalitions, we will see that, with our algorithm, coalitions tend to be less impacted by random failures.
